Multiset-trie data structure

### 2023-02-22 tex/tex/s_operations.tex
responses added; two XXX left; s_operations.tex updated.

@@

\subsection{Sub-multiset existence} \label{s:subexists}
The function \textsc{submsetExistence}($\mathcal{M},m,dev$) checks if there exists 
a multiset $x$ in $\mathcal{M},$ that satisfies the condition $x\subseteq m$ and 
$| x[i] - m[i] | \leq dev,$ where $1\leq i \leq \sigma.$ 
The function starts with searching for an exact match $x=m$ in $\mathcal{M},$ 
since $m\subseteq m$ by definition of sub-multiset inclusion. If an exact match is 
not found in $\mathcal{M},$ the function uses multiset-trie to find the closest 
(the largest) sub-multiset of $m$ in $\mathcal{M}$ by decreasing the multiplicity of 
elements in $m.$ The parameter $dev$ is used to limit a maximal deviation of 
multiplicity for a particular element in $x$ with respect to $m.$ 
At every level, the function tries to proceed with the largest possible multiplicity of 
an element that is provided by $m.$ However, when the function reaches some level 
where it meets a \emph{Null} node and can not go further using the path provided by 
$m,$ it decreases the multiplicity of an element 
that corresponds to a current level with respect to the specified maximal deviation. 
Thus, the function can decrease the multiplicity of an element or eventually skip it in 
order to find the closest $x\subseteq m.$ The function \textsc{submsetExistence} 
is presented in Algorithm~\ref{alg:subexists}.

@@

\subsection{Super-multiset existence} \label{s:superexists}
The function \textsc{supermsetExistence}($\mathcal{M},m,dev$) checks if there 
exists super-multiset $x$ of a given multiset $m$ in $\mathcal{M},$ such that 
condition $| x[i] - m[i] |\leq dev$ is satisfied, where $1\leq i \leq \sigma.$ By analogy 
to the function \textsc{submsetExistence}, the function \textsc{supermsetExistence} 
starts by searching for an exact match $x=m$ in $\mathcal{M}.$ If an exact 
match is not found in $\mathcal{M},$ the function searches for the closest (the 
smallest) super-multiset $x$ of $m$ in $\mathcal{M}$ by increasing multiplicity 
of elements in $m.$ At every level, the function tries to proceed with the smallest 
possible multiplicity of an element that is provided by $m.$ However, when the function 
reaches some level where it meets a \emph{Null} node and can not go further using 
the path provided by $m,$ it increases the multiplicity of an element that corresponds to a 
current level according to the deviation parameter $dev.$ Thus, the function \textsc{supermsetExistence} 
can increase multiplicity of an element up to $n-1,$ where $n$ is the degree of 
a node in $\mathcal{M},$ to find the closest super-multiset $x\supseteq m$ in 
$\mathcal{M}.$ The function \textsc{supermsetExistence} is presented in 
Algorithm~\ref{alg:superxists}.

>>>>

The parameter $dev$ is used to specify the maximal deviation in the multiplicity
of multiset containment operations. It is utilized to limit the search in multiset
containment queries to the sub-multisets and super-multisets that are
the closest to the input multiset $m$. In addition, we use $dev$ for
the implementation of multiset similarity search that, given $m$, retrieves
from $\mathcal{M}$ all sub-multisets or super-multisets that are similar to $m$
with respect to the deviation $dev$.

@@

\subsection{Sub-multiset and super-multiset existence}
\label{s:subexists} \label{s:superexists}
The functions \textsc{submsetExistence} and \textsc{supermsetExistence} are
symmetrical in the following sense. Let a multiset $m$ represent the borderline
in $\mathcal{M}$ defined by a path from the root to a leaf by following
the elements from $m$. The operation \textsc{submsetExistence} searches
the left part of $\mathcal{M}$ and the operation \textsc{supermsetExistence}
the right part of $\mathcal{M}$.

The function \textsc{submsetExistence}($\mathcal{M},m,dev$) checks if there exists 
a multiset $x$ in $\mathcal{M},$ that satisfies the condition $x\subseteq m$ and 
$| x[i] - m[i] | \leq dev,$ where $1\leq i \leq \sigma.$ 
The function starts with searching for an exact match $x=m$ in $\mathcal{M},$ 
since $m\subseteq m$ by definition of sub-multiset inclusion. If an exact match is 
not found in $\mathcal{M},$ the function uses multiset-trie to find the closest 
(the largest) sub-multiset of $m$ in $\mathcal{M}$ by decreasing the multiplicity of 
elements in $m.$ The parameter $dev$ is used to limit a maximal deviation of 
multiplicity for a particular element in $x$ with respect to $m.$ 
At every level, the function tries to proceed with the largest possible multiplicity of 
an element that is provided by $m.$ However, when the function reaches some level 
where it meets a \emph{Null} node and can not go further using the path provided by 
$m,$ it decreases the multiplicity of an element 
that corresponds to a current level with respect to the specified maximal deviation. 
Thus, the function can decrease the multiplicity of an element or eventually skip it in 
order to find the closest $x\subseteq m.$ The function \textsc{submsetExistence} 
is presented in Algorithm~\ref{alg:subexists}.

@@

%\subsection{Super-multiset existence} \label{s:superexists}
The function \textsc{supermsetExistence}($\mathcal{M},m,dev$) checks if there 
exists super-multiset $x$ of a given multiset $m$ in $\mathcal{M},$ such that 
condition $| x[i] - m[i] |\leq dev$ is satisfied, where $1\leq i \leq \sigma.$
Symmetrically to the function \textsc{submsetExistence}, the function
\textsc{supermsetExistence} searches first for an exact match $x=m$ in
$\mathcal{M}.$ If such $x$ does not exist in $\mathcal{M},$ then
the function searches on the right side of the borderline (an exact match)
defined by $m$. Since we would like to find the closest (the smallest)
super-multiset we increase the multiplicity of elements in $m$ at every
level of $\mathcal(M)$ starting with the multiplicities of $m.$
The function \textsc{supermsetExistence} is presented in
Algorithm~\ref{alg:superxists}.
